Water desalination using polyelectrolyte hydrogel.

### 2022-09-03 Creta_ecis2022/presentation/beamer.tex
beamer

\newcommand{\cl}{\mathrm{Cl^-}}
\newcommand{\br}{\mathrm{Br^-}}
\newcommand{\na}{\mathrm{Na^+}}
\newcommand{\h}{\mathrm{H^+}}
\newcommand{\ka}{\mathrm{K^+}}
\newcommand{\oh}{\mathrm{OH^-}}
\newcommand{\ca}{\mathrm{Ca^{2+}}}
\newcommand{\mg}{\mathrm{Mg^{2+}}}
\newcommand{\so}{\mathrm{SO_4^{2-}}}
\newcommand{\cs}{c_{\mathrm{s}}}
\newcommand{\gel}{^{gel}}
\newcommand{\Vgel}{V\gel}
\newcommand{\NA}{N_{\mathrm{A^-}}}
\newcommand{\pK}{\mathrm{p}K}
\newcommand{\pH}{\mathrm{pH}}
\newcommand{\cp}{c_\mathrm{p}}
\newcommand{\kT}{kT}
\usepackage{subfig}
\usetheme[progressbar=frametitle]{metropolis}
\usepackage{appendixnumberbeamer}

@@

\section[Model]{Model of the gel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Model of the gel}
  \begin{columns}[T,onlytextwidth]% COLUMNS
    \column{0.35\textwidth}
\begin{figure}
\includegraphics[height=4.5cm]{figures/gel_donnan.png}
\end{figure}

@@

\section{The model of a polyelectrolyte gel.}
\subsection{Langevin dynamics.}
\begin{frame}{Langevin dynamics. }
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.4\textwidth}
			\begin{figure}
				\includegraphics[height=4.5cm]{figures/snapshot_cut.png}
				\caption{The snapshot of the hydrogel model for Langevin dynamics}
			\end{figure}   
		\column{0.01\textwidth}
		\column{0.6\textwidth}

@@

{
\begin{frame}{Grand-reaction ensemble.}
	\textbf{Grand canonical ensemble}\\ 
	\vspace{1cm}
	The free energy of the grand-canonical ensemble for single particle type
	\begin{equation*}
		\boxed{
		\Omega=E-TS+\mu N\label{eq:Omega-GC}}
	\end{equation*}
	The entropy $S$ expands via Boltzmann formula
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
			\begin{equation*}
				S=k_{B}\ln\frac{V^{N}}{N!}\label{eq:entropy}
			\end{equation*}
		\column{0.5\textwidth}
			\begin{equation*}
				\Omega=E-k_BT\ln\frac{V^N}{N!}+\mu N \label{eq: Omega_GC}
			\end{equation*}
	\end{columns} % COLUMNS
	The change of free energy associated with a sngle particle exchange is 
	\begin{equation*}
		\boxed{
		\Delta\Omega=k_BT\ln\left(V^{\xi}\frac{N!}{\left(N+\xi\right)!}\right)+\xi\mu+\Delta E\label{eq: DeltaG GC}}
	\end{equation*}
	{\tt accept if $\mathcal{R}^{\xi}<e^{\Delta\Omega/k_BT}$}
\end{frame}
}

@@

	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=4.cm]{figures/standard_states.pdf}
			\end{figure} 
		\column{0.5\textwidth}	
			\textbf{Moderate pH conditions}\\ 
			\vspace{1cm}
			The reaction of an acidic unit 
			\begin{equation*}
				\mathrm{HA}\stackrel{K}{\leftrightarrows}\mathrm{A^-}+\mathrm{H^+}\label{eq: acid reaction}
			\end{equation*}
	Is happening only simultaneously with one of these two
	\begin{eqnarray*}
		\h&\leftrightarrows&\na \label{eq:hna} \\
		2\h&\leftrightarrows&\ca \label{eq:hca}
	\end{eqnarray*}

	\end{columns} % COLUMNS
\begin{eqnarray*}
\mathrm{HA}\stackrel{K'}{\leftrightarrows}\mathrm{A}^{-}+\na, &K' = K \exp(\mu_\h-\mu_\na) \\
2\mathrm{HA}\stackrel{K''}{\leftrightarrows}2\mathrm{A}^{-}+\ca, &K'' = K \exp(2\mu_\h-\mu_\ca)
\end{eqnarray*}
\end{frame}

>>>>

\newcommand{\cl}{\mathrm{Cl^-}}
\newcommand{\br}{\mathrm{Br^-}}
\newcommand{\na}{\mathrm{Na^+}}
\newcommand{\h}{\mathrm{H^+}}
\newcommand{\ka}{\mathrm{K^+}}
\newcommand{\oh}{\mathrm{OH^-}}
\newcommand{\ca}{\mathrm{Ca^{2+}}}
\newcommand{\mg}{\mathrm{Mg^{2+}}}
\newcommand{\so}{\mathrm{SO_4^{2-}}}
\newcommand{\cs}{c_{\mathrm{s}}}
\newcommand{\gel}{^{gel}}
\newcommand{\Vgel}{V\gel}
\newcommand{\NA}{N_{\mathrm{A^-}}}
\newcommand{\pK}{\mathrm{p}K}
\newcommand{\pH}{\mathrm{pH}}
\newcommand{\cp}{c_\mathrm{p}}
\newcommand{\muna}{\mu_\mathrm{Na^+}}
\newcommand{\mucl}{\mu_\mathrm{Cl^-}}
\newcommand{\muca}{\mu_\mathrm{Ca^{2+}}}
\newcommand{\muh}{\mu_\mathrm{H^+}}
\newcommand{\mua}{\mu_\mathrm{A^-}}
\newcommand{\muha}{\mu_\mathrm{HA}}
\newcommand{\muoh}{\mu_\mathrm{OH}}
\newcommand{\cna}{c_\mathrm{Na^+}}
\newcommand{\ccl}{c_\mathrm{Cl^-}}
\newcommand{\cca}{c_\mathrm{Ca^{2+}}}
\newcommand{\ch}{c_\mathrm{H^+}}

\newcommand{\nna}{N_\mathrm{Na^+}}
\newcommand{\ncl}{N_\mathrm{Cl^-}}
\newcommand{\nca}{N_\mathrm{Ca^{2+}}}

\newcommand{\kT}{kT}
\usepackage{subfig}
\usetheme[progressbar=frametitle]{metropolis}
\usepackage{appendixnumberbeamer}

@@

\section{The model of a polyelectrolyte gel.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Model of the gel}
  \begin{columns}[T,onlytextwidth]% COLUMNS
    \column{0.35\textwidth}
\begin{figure}
\includegraphics[height=4.5cm]{figures/gel_donnan.png}
\end{figure}

@@

\subsection{Grand-cannonical ensemble.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Grand-cannonical ensemble.}
	\begin{columns}[T,onlytextwidth]% COLUMNS
	\column{0.5\textwidth}
	\column{0.5\textwidth}
	The free energy of the grand-canonical ensemble exchanging ion pair with the bath
	\begin{equation*}
		\boxed{
		\Omega=E-TS+\mu N}
	\end{equation*}
	The entropy $S$ expands via Boltzmann formula
		\begin{equation*}
			S=k_{B}\ln\frac{V^{N}}{N!}\label{eq:entropy}
		\end{equation*}
	\end{columns}% COLUMNS		
	The change of free energy associated with a single particle exchange is 
	\begin{equation*}
		\boxed{
		\Delta\Omega=k_BT\xi\ln V \left(N+\theta(\xi)\right)+\xi\mu+\Delta E\label{eq: DeltaG GC}}
	\end{equation*}
	{\tt accept if $\mathcal{R}^{\xi}<e^{\Delta\Omega/k_BT}$}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Gibbs ensemble.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Gibbs ensemble.}
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
		\begin{figure}[t]
			{\includegraphics[width=0.9\columnwidth]{{figures/simgibbs}.pdf}}
		\end{figure}
		\column{0.5\textwidth}
			The free energy of the grand-canonical ensemble for single particle type
	\begin{equation*}
		\boxed{
		\Omega=E_1+E_2-TS}
	\end{equation*}

	\begin{equation}
		S=k_B \ln \frac{V_1^{N_1}}{N_1!}\frac{V_2^{N_2}}{N_2!}
	\end{equation}
	\end{columns}% COLUMNS		
	The change of free energy associated with a single particle exchange is 
	\begin{equation*}
		\boxed{
		\Delta\Omega=k_BT\xi \ln\left(\frac{V_1}{V_2}\frac{N_2+\theta(-\xi)}{N_1+\theta(\xi)}\right)+\Delta E_1 +\Delta E_2\label{eq: DeltaG GC}}
	\end{equation*}
	{\tt accept if $\mathcal{R}^{\xi}<e^{\Delta\Omega/k_BT}$}

\subsection{Langevin dynamics.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Langevin dynamics. }
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.4\textwidth}
			\begin{figure}
				\includegraphics[height=4.5cm]{figures/snapshot_cut.png}
				\caption{The snapshot of the hydrogel model for Langevin dynamics}
			\end{figure}   
		\column{0.01\textwidth}
		\column{0.6\textwidth}

@@

}

@@
